A_pilot_1

### 2018-09-12 docs/A_pilot_1.Rmd
added the pilot experiments R stuff
typo fix

The experiment used subitizable numbers as well as bigger numbers. The instructions had the form: _Choose the square with {{few, many},{two, three, four, five, six, seven, eight, nine}} dots._ The variables were: subitizability; vagueness; target_size; gap_size; side (i.e., which side was the bigger number on?)

```{r "read the data from file, add some vars", message=FALSE}
# read in the data from file
din <- read_delim("data.txt", delim="\t")

>>>>

The experiment used subitizable numbers as well as bigger numbers. The instructions had the form: _Choose the square with (few, many), (two, three, four, five, six, seven, eight, nine) dots._ The variables were: subitizability; vagueness; target_size; gap_size; side (i.e., which side was the bigger number on?)

```{r "read the data from file, add some vars", message=FALSE}
# read in the data from file
din <- read_delim("A_pilot_1_data/data.txt", delim="\t")
